Raft Distributed Consensus Algorithm over WebRTC (Web Real-Time Communication)

### 2015-09-12 research_class/paper.tex
Usage: "traverse" doesn't need "through"

\begin{enumerate}
\item \emph{security (privacy)}: application state and user messages
    may need to traverse directly from browser to browser rather than
    traversing through a server.
\item \emph{locality}: the nature of the application may allow
    clusters of applications that are nearby on a network (e.g.
    intranet) to communicate and coordinate directly rather than
    passing all messages and state through a server back-end which may
    be considerably more remote.
\item \emph{bandwidth and scale}: a distributed browser based
    application may be able to avoid expensive bandwidth into and out
    of the backend data-center by passing messages and state directly
    between browsers.  Depending on the design of the application this
    may also enable better scalability then a more centralized model.
\end{enumerate}

@@

\begin{enumerate}
\item \emph{Consistent order secure chat}: a chat room system where
    all users see the same message history but the messages never
    traverse through a central server and there is no central arbiter
    of trusth. The application code itself may still be delivered from
    a central web service. This is the use case that was implemented
    for this paper.
\item \emph{Private multiuser document editing/whiteboard system}:
    Google Docs, among other examples has demonstrated a powerful
    model for collaborative document creation. However, these systems
    all use a centralized servers to coordinate shared state and
    handle browser-to-browser communication. %TODO/CITE
    Using a Raft over WebRTC could enable applications with similar
    functionality but without the central coordination and
    communication.
\item \emph{Browser based network games}: most network games have
    certain states that must be agreed upon by all nodes (e.g. avatar
    dead or alive, etc). This can be achieved with Raft over WebRTC
    without requiring any data to traverse a central server. In
    addition to reducing browser to server bandwidth requirements,
    this may also allow lower latency gaming if game instances are
    partitioned into clusters based on latency.
\end{enumerate}

>>>>

\begin{enumerate}
\item \emph{security (privacy)}: application state and user messages
    may need to traverse directly from browser to browser rather than
    traversing a server.
\item \emph{locality}: the nature of the application may allow
    clusters of applications that are nearby on a network (e.g.
    intranet) to communicate and coordinate directly rather than
    passing all messages and state through a server back-end which may
    be considerably more remote.
\item \emph{bandwidth and scale}: a distributed browser based
    application may be able to avoid expensive bandwidth into and out
    of the backend data-center by passing messages and state directly
    between browsers.  Depending on the design of the application this
    may also enable better scalability then a more centralized model.
\end{enumerate}

@@

\begin{enumerate}
\item \emph{Consistent order secure chat}: a chat room system where
    all users see the same message history but the messages never
    traverse a central server and there is no central arbiter
    of trusth. The application code itself may still be delivered from
    a central web service. This is the use case that was implemented
    for this paper.
\item \emph{Private multiuser document editing/whiteboard system}:
    Google Docs, among other examples has demonstrated a powerful
    model for collaborative document creation. However, these systems
    all use a centralized servers to coordinate shared state and
    handle browser-to-browser communication. %TODO/CITE
    Using a Raft over WebRTC could enable applications with similar
    functionality but without the central coordination and
    communication.
\item \emph{Browser based network games}: most network games have
    certain states that must be agreed upon by all nodes (e.g. avatar
    dead or alive, etc). This can be achieved with Raft over WebRTC
    without requiring any data to traverse a central server. In
    addition to reducing browser to server bandwidth requirements,
    this may also allow lower latency gaming if game instances are
    partitioned into clusters based on latency.
\end{enumerate}
